Forecasting the 2024 US Presidential Election: A Poll-Based Approach

### 2024-10-19 paper/paper.qmd
Update data cleaning process

```{r}
data %>% 
  select(numeric_grade, pollscore) %>% 
  filter(complete.cases(.)) %>% 
  cor()
```

```{r}
sort(unique(data$sample_size)) %>% 
  summary()
```

```{r}
data %>% 
  filter(numeric_grade >= 2.0) %>% 
  skim()
```

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

@@

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}

Talk way more about it.

>>>>

```{r}
model <- data %>%
  filter(numeric_grade >= 2.0, candidate_name == "Kamala Harris") %>%
  lm(pct ~ numeric_grade + days_towards_election, data = .)

# Get the summary of the model
summary(model)
```

"pollster"                 
"sponsors"                               
"numeric_grade"             
"pollscore"                 
"methodology"               
"transparency_score"       
"state"                     
"start_date"                
"end_date"                 
"sponsor_candidate"         
"sponsor_candidate_party"        
"question_id"               
"sample_size"               
"population", "population_full",
"tracking", "notes"                     
"source"                    
"internal"                  
"partisan"                 
"race_id"                                 
"ranked_choice_reallocated" 
"ranked_choice_round"       
"hypothetical"              
"party"                    
"answer"                   
"candidate_name"            
"pct"

```{r}
selected_columns <- c(
  "pollster", 
  "sponsors", 
  "numeric_grade", 
  "pollscore", 
  "methodology", 
  "transparency_score", 
  "state", 
  "start_date", 
  "end_date", 
  "sponsor_candidate", 
  "sponsor_candidate_party", 
  "question_id", 
  "sample_size", 
  "population", 
  "population_full",
  "tracking", 
  "notes", 
  "source", 
  "internal", 
  "partisan", 
  "race_id", 
  "ranked_choice_reallocated", 
  "ranked_choice_round", 
  "hypothetical", 
  "party", 
  "answer", 
  "candidate_name", 
  "pct"
)
data %>% 
  select(all_of(selected_columns))
```

@@
